SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-11-12 docs/questioning.tex
pass in abstract

  Some of the most dangerous web application attacks, like Cross-Site
  Scripting and {\sc sql} injection, exploit the oversight of
  programmers that develop applications that may accept and process
  data of uncertain origin without appropriate validation and / or
  filtering. Such attacks, relying on source code injection
  vulnerabilities, have been constantly topping the lists of the
  various security bulletin providers despite the numerous
  countermeasures that have been proposed over the past 15 years.

  In this paper we systematize the existing knowledge regarding
  various defense mechanisms against source code injection by setting
  up a model that highlights the key weaknesses behind such attacks
  and provides a common perspective for the different defenses.

  We then categorize and analyze the various defense mechanisms that
  have been developed. Our analysis is based on accuracy, performance,
  deployment, security and availability. Especially notable is
  accuracy, as our findings show that there are many defense
  mechanisms that are tested in a poor manner. In addition, we observe
  that there are mechanisms that can be bypassed by attackers that
  know how the mechanisms work.

  By comparing the existing defenses and identifying their common
  characteristics, we help researchers and practitioners to choose or
  modify a mechanism according to their needs as well as designers of
  new approaches in developing more efficient mechanisms.

>>>>

  Some of the most dangerous web application attacks, such as Cross-Site
  Scripting and SQL injection, exploit vulnerabilities
  in web applications that may accept and process
  data of uncertain origin without proper validation or
  filtering, allowing the injection and execution of
  dynamic or domain-specific language code.
  These attacks have been constantly topping the lists of
  various security bulletin providers despite the numerous
  countermeasures that have been proposed over the past 15 years.

  In this paper, we systematize the existing knowledge on
  various defense mechanisms against source code injection attacks by proposing
  a model that highlights the key weaknesses that enable these attacks,
  and provides a common perspective for the different defenses.
  We then categorize and analyze the various defense mechanisms that
  have been developed, based on their accuracy, performance,
  deployment, security, and availability properties.
  Accuracy is of particular importance, as our findings show that many defense
  mechanisms have been tested in a poor manner. In addition, we observe
  that some mechanisms can be bypassed by attackers with knowledge
  of how the mechanisms work.
  By comparing the existing defenses and identifying their common
  characteristics, we help researchers and practitioners to choose or
  modify defenses according to their needs, as well as designers of
  new approaches in developing more effective mechanisms.
